Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-12 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Optimization Analysis}
For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The covariance matrix is initialized uniformly with standard deviation \mf{ADD HERE}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary. }
    \label{BucklingOptimization}
\end{figure}

>>>>

\section{Optimization Analysis}
For the optimization portion of the work presented in the main article we used a stochastic, derivative-free evolutionary method called Covariance Matrix Adaptation Evolution Strategy (CMA-ES) implementation in Python \citep{hansen2003}. The algorithm parameters (continuous input variables) are: the structure's mass ratio $\lambda$ (keeping the total structure volume constant, as well as distributing the mass evenly through all diagonal and non-diagonal elements respectively) and the separation of the even numbered diagonal elements from the non-diagonal junction. Separate instances of the optimization algorithm are analyzed for different numbers of diagonal reinforcements. For simulations with odd number of diagonal re-enforcements, only an even number of diagonals are separated while keeping one diagonal going through the non-diagonal junction in order to ensure geometry symmetry. The algorithm's initial values are chosen to be in the center of the design space, namely, $\lambda=1$ and diagonal separation$=0.5*L$. The optimization is run under a uniaxial loading condition in the direction parallel non-diagonal elements. In order to maintain reasonable computational complexity, the optimization was run on the unit cell constructed using one dimensional beams with node seeding of at least 1/20 of each beam length. The covariance matrix is initialized uniformly with standard deviation \mf{ADD HERE}.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uni-axial loading condition.}
    \label{BucklingOptimization}
\end{figure}
